# Business Analyst in Tech {-}

In this chapter we will cover the following content:

- what does the role of business analyst entail in the tech industry
- what skill-sets are required and preferred
- what is a day-to-day like for a business analyst in Tech
- what is the difference between business analyst, data analyst, data scientist, and machine learning engineer
- how does they work in teams (with engineers and scientists, with stakeholders, with product managers, etc.)


## Summary {-}

A business analyst (BA) in a tech company utilizes data analytics, business sense, and problem solving skills to drive key business decisions. One’s responsibilities typically include defining metrics, developing reports on internal/external data, performing ad-hoc data analytics, and designing dashboards. Both technical and soft skills are important for a business analyst in tech. An analyst often needs to work with cross-functional teams, communicate with customers and stakeholders, give presentations on data insights, and collaborate with the engineers and researchers. It’s also important to note that a data analyst is often synonymous with a business analyst in certain companies, and many analyst positions in tech share the same responsibility as a business analyst but are given different, often more specific, titles for the specific areas they focus on.


## Education & Background {-}

* Bachelor's degree in Business, Engineering or a related field is required.

* Normally requires 2+ years of relevant experience with data analytics in business context and statistical analysis


## Skill Sets {-}

**Hard Skills:**

* SQL (basic query, join methods, aggregate functions, window functions) for ETL & data mining

* Advanced Excel (Pivot Tables, Power Pivots, VBA, Power Query, etc.)

* Python (basic Python data structures, list and string manipulation)

* AB Testing (Basic stats knowledge, hypothesis testing)

* Preparing and executing presentation slides on business level data

**Soft Skills:**

* Designing business metrics

* Problem solving skills

* Communication skills


## Salary {-}

Industry Entry Level Average Salary: $97,112/yr

* Average Base: $70,921/yr

* Average Bonus: $26,191/yr

### Tier 0 Tech Companies {-}
```{r, echo=FALSE}
tier0 = read.csv("csv/tech_tier0.csv")
knitr::kable(tier0, "pipe", col.names=c("Company", "Avg Annual Compensation", "Avg Annual Base", "Avg Annual Bonus"))
```

### Tier 1 Tech Companies {-}
```{r, echo=FALSE}
tier1 = read.csv("csv/tech_tier1.csv")
knitr::kable(tier1, "pipe", col.names=c("Company", "Avg Annual Compensation", "Avg Annual Base", "Avg Annual Bonus"))
```

### Tier 2 Tech Companies {-}
```{r, echo=FALSE}
tier2 = read.csv("csv/tech_tier2.csv")
knitr::kable(tier2, "pipe", col.names=c("Company", "Avg Annual Compensation", "Avg Annual Base", "Avg Annual Bonus"))
```

### Tier 3 Tech Companies {-}
```{r, echo=FALSE}
tier3 = read.csv("csv/tech_tier3.csv")
knitr::kable(tier3, "pipe", col.names=c("Company", "Avg Annual Compensation", "Avg Annual Base", "Avg Annual Bonus"))
```


## Work life Balance {-}

Industry Average Working Hours: 8-10 hrs

